### 2015-12-10 paper/4-performance.tex
Added brief explanation of benchmarks; added eps version of cores class diagram

\subsection{Benchmarks}
%TODO

>>>>

\subsection{Benchmarks}
We use a selection of benchmarks, based on those found in the literature.
Three different types of benchmark are defined:
\begin{enumerate}
    \item \textit{Queue} model, based on the HI model of DEVStone~\cite{DEVStone}, creates a chain of atomic models, which are hierarchically nested in each other.
          It contains two parameters: width and depth.
          Width determines the number of atomic models in a single level, and depth determines the number of levels.
          An example for width 3 and depth 2 is shown in Figure~\ref{fig:queue}.
    \item \textit{HighInterconnect} model, an exaggeration of the HI model of DEVStone~\cite{DEVStone}, creates a set of atomic models, which are all directly connected to each other.
          Each model has a single input and output port, but each output port is connected to each input port\footnote{Except, of course, that the output and input port of a single model are not connected to each other.}.
    \item \textit{PHOLD} model, presented by~\cite{PHOLD}.
          It creates a set of $n$ atomic models, similar to HighInterconnect, but each model has exactly $n-1$ output ports.
          Couplings are made such that each atomic model is directly connected to each other atomic model, but it can \textit{narrowcast} instead of \textit{broadcast}ing.
          These $n$ models are further equally distributed over $k$ coupled models.
\end{enumerate}

We opted to deviate from the DEVStone benchmark, as DEVStone tended towards unrealistic models because all internal and external transitions occur simultaneously.
In our benchmark models, there is always the option for simultaneous transition functions (\textit{fixed time advance}), or scattered transition functions (\textit{random time advance}).
Furthermore, they defined the use of an artificial load function, which easily skews the result, making the actual simulation algorithm barely comparable.

%TODO figures! I have them lying around somewhere I guess... still need to search for them
